Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-03-08 draft.tex
Added a few sentences about the designer not needing prior knowledge of mechanism parameters and how to deal with fabrication errors.  This is in response to some of I-Ming's comments that I missed earlier.

>>>>

{\color{ForestGreen}
Our treatment of design involves dealing with algebraic equations rather than geometric constructions.
This makes our method technically simple for designers without prior knowledge of mechanism parameters, removing the need for geometric creativity.
Furthermore, by generating multiple design options, a designer is better equipped to account for secondary requirements, such as sensitivity to fabrication errors.
}
